Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
MCS instances

What would happen if we used our approach to solve the maximum common induced problem? We could
simply start at $k = 0$, and increase $k$ until a solution is found. This would be tackling the
problem in the opposite direction from existing approaches, which work by attempting to construct
larger and larger solutions. The dotted lines in \cref{figure:runtimes} show this approach: the $k
\downarrrow$ is our algorithm, whilst ``MCS'' and ``clique'' are the two algorithms discussed in ??.
Bearing in mind the disclaimer in \cref{section:setup} regarding instances not fitting in RAM, we
see that our approach is able to close over twice as many of these instances as the previous state
of the art. (The same conclusion holds even if every instance which is satisfiable with $k = 0$ is
removed from the dataset.)

>>>>

What would happen if we used our approach to solve the maximum common induced problem? We could
simply start at $k = 0$, and increase $k$ until a solution is found. This would be tackling the
problem in the opposite direction from existing approaches, which work by attempting to construct
larger and larger solutions. The dotted lines in \cref{figure:runtimes} show this approach: the $k
\downarrow$ is our algorithm, whilst ``FC'' and ``clique'' are the two algorithms discussed in ??.
Bearing in mind the disclaimer in \cref{section:setup} regarding instances not fitting in RAM, we
see that our approach is able to close over twice as many of these instances as the previous state
of the art. (The same conclusion holds even if every instance which is satisfiable with $k = 0$ is
removed from the dataset.)

\begin{figure}[tb]
    \includegraphics*{gen-graph-mcsruntimes.pdf}
    \caption{The cumulative number of maximum common induced subgraph instances solved over time,
    comparing our decreasing $k$ approach with two state of the art
    solvers.}\label{figure:mcsruntimes}
\end{figure}

What about if we use instances designed for the maximum common subgraph problem? In
\cref{figure:mcsruntimes} we again compare these approaches, but using the first ten instances from
each family of a standard benchmark set
\citep{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}, selecting undirected, unlabelled
graphs with up to 50 vertices---this gives us a total of 4,110 instances. In these instances the
number of vertices in the pattern and target graphs is the same, which is not ideal for our
algorithm (although our invariants are still effective in many cases). Nonetheless, we are by a
small margin the single strongest solver. Interestingly, our algorithm tends to have complementary
performance to the other two approaches (which are much more correlated), which suggests that there
is scope for an algorithm which runs both an upper bound and a constructive, lower bound approach
simultaneously or in parallel, stopping when the two bounds meet in the middle.
